\chapter{Resource Requirements}\label{S1CS}
During the initial meetings between the project groups, it was found that the
existing client/database communications system was incomplete and not of a high
enough quality for us to dedicate development time in order to attempt to
improve it. As such, it was decided, that the groups responsible for the
database (SW613 and SW615) would be tasked to develop a new system, which should
make use of the principles described in the REST model (Representational State
Transfer).\nl

As a part of developing this new system, the REST groups (SW613 and SW615)
requested a meeting the groups responsible for the GIRAF applications (SW609 and
SW610), in order to determine the database resource requirements for the
individual applications. Considering the incomplete state of the previous
system, this information was needed in order to model the server and client
libraries such that they would be able to transfer all necessary data to the
applications.\nl

\section{Initial Requirement Analysis}
As our group (SW609) is responsible for the \textc{Launcher} application and the
\textc{pictosearch-lib} library, we were tasked with analyzing the relevant
code before the scheduled meeting, in order to determine what database
resources would be necessary for these applications/libraries. These tasks are
presented in \autoref{TaS1} as T636, T646, and T647.\nl

In our case, we mostly determined the requirements testing the \textc{Launcher}
and \textc{pictosearch-lib} through general use. Based on this testing, and a
superficial analysis of the code, we determined the following requirements:

\begin{itemize}
  \item User (Guardian or Citizen)
  	\begin{itemize}
  		\item Name
  		\item UserID
  		\item Picture (Icon) 
	\end{itemize}
\end{itemize}




Intro, purpose (report part), Tasks, Meeting 1, Meeting 1 results, Initial
diagrams, Our work based on M1, Meeting 2, Meeting 2 results.




T636 - Weekplaner: Identify Functional Requirements\\
T646 - Identify Apps required resources\\
T647 - Document Applications Database Requirements\\


These chapters should mainly be focus on the final state of affairs and not the
steps along the way. They should be the ideal starting point for new developers
to continue the development on the system.\\


See T647 and T646\\
OOAD ideas\\
REST constraints\\

Notes 1 meeting.\\
\begin{itemize}
  \item At the meeting we started by taking about the different resources that we need
for our apps.
\begin{itemize}
  \item Users
  \item Pictograms
\end{itemize}
\item There is a diagram somewhere of the resources.
\item Then we talked about which resources that should be able to do something
from rest (I mean it should be update, delet, creat but I am not 100p sure).
Mabye ask Thomas for the stuffs.
\end{itemize}

