\chapter{Launcher Guide}\label{WikiLauncher}

\textbf{IMPORTANT - There are many ToDo's in the code, we have added most of
them so that the developers next year know what they should work on and fix. We
have also kept the ToDo's from when we received the code, but only if we have
not fixed them.}

\subsubsection{Features}
\begin{itemize}
  \item The \textc{Launcher} is able to launch the apps a user can access. If
  the app is not installed it opens google play such that it can be installed easily.
  \item The settings part of the \textc{Launcher} should work, but somehow when
  we put settings up, they are not the same we get next time we start the app. This
  also means that grayscale only works in the \textc{Settings activity}. This
  should be fixed together with the groups who will continue the work on
  \textc{REST}, both the \textc{Server} and the \textc{Client-Lib}.
  \item The Settings for the list of apps that a user can access does not work
  because we get a \textc{stackoverflow} from \textc{REST} and as such the code
  which makes the resource \textc{PutRequest} is disabled and a \textc{ToDo} has
  been added in both classes, this should be fixed together with the new
  \textc{REST} groups.
  \item The login screen works, but is missing a way to handle a
  \textc{Department} login, such that when a \textc{Department} login is used,
  the list of \textc{Guardians} in the \textc{Department} is used to select
  which \textc{Guardian} is used in the \textc{Launcher}. This needs to be fully
  supported by the \textc{REST Server} and \textc{REST Client-Lib}.
\end{itemize}

\subsubsection{Short into to the REST conversion}
\begin{itemize}
  \item We have removed \textc{SharedPreference} from all the classes such that
  no user information is stored in such a way. This means that all classes where the
  user was retrieved from a \textc{SharedPreference} does not work and have thus
  been changed to either use a \textc{GetRequest} for a user or receive
  the user from a class higher up.
  \item When using the user it should come from a \textc{GetRequest} or from a
  higher class which has just used a \textc{GetRequest}. The developer
  should \textbf{NEVER EVER} use the user without first having received the
  latest version from a \textc{GetRequest}. 
  \item We now pass the user from \textc{Intent} to \textc{Intent} instead of
  the passing the \textc{Username}.
  \item Remember when creating \textc{Requests} that the \textc{ErrorResponse}
  can be \textc{null} \textbf{or} the \textc{networkResponse} can be
  \textc{null}, this should be checked for in each request. We have not done
  this in every request, but this should be fixed by next years developers.
\end{itemize}

\subsubsection{Missing / Non-finshed features}

\begin{itemize}
  \item Grayscale should also be made to work on the login screen, this
  could be done though the use of a \textc{SharedPreference} where the last
  value of grayscale from the last logged in user will be stored and
  \textbf{ONLY} used in the login screen.
  \item Each request should check if the error response or networkResponse is
  null before using them.
  \item \textc{Settings} should be fixed. The \textc{PutRequest} for resources
  is currently not working and the settings for apps in general need more work.
  \item Better icons for the download of missing apps.
  \item \textc{Dialogs} should be in grayscale if the rest of the
  \textc{Launcher} is in grayscale, this bug involves both the \textc{Launcher}
  and \textc{Component-Lib}.
  \item It should not be possible to change user through settings. The changed
  to user should be logged out and the orginal user should be logged in again.
  \item There should be a better way to find the correct icon for an app,
  instead of going through the entire list of apps and comparing it with an
  \textc{Activity} name.
\end{itemize}

\subsubsection{Repository}
http://git.giraf.cs.aau.dk/Giraf17-AndroidApps/launcher |
Launcher

\subsubsection{Dependencies}
\begin{itemize}
  \item com.android.support:support-v4:23.1.1
  \item fr.avianey.com.viewpagerindicator:library:2.4.1 
  \item com.jakewharton:disklrucache:2.0.2 (because of rest)
  \item com.android.volley:volley:1.0.0 (because of rest)
  \item com.google.code.gson:gson:2.8.0 (because of rest)
  \item giraf-component-lib
  \item rest-api-client-lib
  \item rest-models
  \item showcaseview-lib
\end{itemize}