\chapter{User Stories}
\section{Birken 15th of February 2017}\label{BirkenUserStories1502}
\begin{enumerate}
  \setlength\itemsep{0em}
  \item As one of the children who use the system, i want the system to be as
  stable as possible, as my mental problems require that of the tools which i use.
  \item As a pedagogue I want the ability to replace pictures and icons for the children in the system.
  \item As a pedagogue, it is very important to be able to create a weekly
  schedule and manage the tasks the children can see at any given time.
  \item As a user of the system, the response time is an important factor.
  \item As a pedagogue I would like the ability to access the schedules of the kids’ tablets remotely.
  \item As a user of the system, I’d like the interface to be simple, things should never be more than 2-3 taps away.
  \item As a pedagogue, I would like the option of adding placeholder tasks, which can then be changed to something else later. This enables the pedagogues to add tasks to a kid’s schedule later on.
  \item As a pedagogue, I would like to schedule a day by copying another day.
  \item As a pedagogue, I would like to schedule a day using templates.
  \item As a pedagogue, I would like to have certain keywords which i can use to search for pictures by category.
  \item As a user, I would like to be made visually aware of any potential changes made in the schedule.
  \item As a user, I would like to have a way of visualising the order of the tasks, i.e. explicitly numbering the tasks, because some kids prefer explicit ordering.
  \item As a legal guardian, i would like the option to add notes about the individual children, which will then be available to the pedagogues.
  \item As a pedagogue, i would like the option to add notes about the individual children, which will then be available to other pedagogues.
  \item As a pedagogue and or legal guardian I would like the more complicated tasks to expand into sub-tasks when pressed.
\end{enumerate}

\newpage
\section{Egebakken 22nd of March 2017}
\subsection*{General}

\begin{enumerate}
  \setlength\itemsep{0em}
  \item As a user of the system, I would like the system to move back to the nearest stable state when the app crashes.
  \item As a guardian I would like the option to toggle between grayscale and fully colored in the system for a citizen.
  \item As a user of the system I would like the option to toggle between grayscale and fully colored in the system.
  \item As a guardian I would like a video I can use for more advanced tasks such as creating schedules etc.
\end{enumerate}

\subsection*{Launcher}
\begin{enumerate}
  \setlength\itemsep{0em}
  \item As a guardian I would like the login button to let a citizen tap to log in as a citizen, and hold to login as a guardian, only providing login information at that point.
  \item As a guardian I would like to be able to push a template setup onto a group of citizens for the launcher.
  \item As a guardian I would like the option of adding an app to citizens both as groups, individually or marking a list of citizens.
\end{enumerate}

\subsection*{Login System}
\begin{enumerate}
  \setlength\itemsep{0em}
  \item As a guardian I would like not to have a Quick-Response (QR) codes for login, but a regular password instead.
  \item As a guardian I would like the ability to set a password for specific users of the system.
  \item As a guardian I would like the system to automatically log me out of my account after a set time limit (approx. 20 min).
  \item As a citizen I would like the system to not to log me out automatically.
  \item As a guardian I would like the option to make a specific device always log into a citizen's account without password.
  \item As an institute, we would like to be able to log in as the institute as a whole.
\end{enumerate}

\subsection*{Week Planner}
\begin{enumerate}
  \setlength\itemsep{0em}
  \item As a guardian I would like to add my own pictures as an addition to pictograms, as the citizen might need more specification than what a pictogram allows.
  \item As a guardian I would like to copy an entire day and paste it to one of the other days in the week and modify it, to ease the creation of schedules.
  \item As a guardian I would like to print a list of an entire day for a citizen.
  \item As a guardian I would like to have a premade template schedule I can modify or not use at my own accord.
  \item As a citizen I need the option of having timestamps at/by the pictograms.
  \item As a guardian I would like the ability to mark multiple elements from several days and copy them to a single day.
  \item As a guardian I would like to be warned if I am about to overwrite a complete day by using copy/paste.
  \item As an institution I would like only, the guardians, the parents and the citizen itself to have access to the specific citizen’s schedule.
  \item As a guardian I believe the red X to mark tasks as cancelled/deleted can be made thinner to avoid shadowing the pictogram.
  \item As a guardian I would like the system to scale from week to day when I rotate the unit.
  \item As a guardian I would like the UI elements to scale icons when rotating the tablet.
  \item As a citizen I would like the pictograms on the day planner to be scrollable when exceeding page length.
\end{enumerate}
