\chapter{Project Context}
The GIRAF project is an ongoing development process, which aims to develop a
number of applications for Android tablets, which are to be used by children
with varying degrees of autism. The project is being developed by bachelor students
at Aalborg University, and has been under development since early 2011. Each
semester, the new bachelor students must work together to analyze the state of
the project, and determine which improvements they intend to implement.\nl

The current implementation of the GIRAF project consists of 10 different
interconnected applications, which are presented below in \autoref{GApps}.


\begin{table}[H]
\centering
\begin{tabular}{|p{3cm}|p{9cm}|}
\hline
Application			& Description \\\hline
Launcher  			& The main application of GIRAF, controls access to other
GIRAF applications. \\\hline 
Sequence	       	& A tool to create a sequence of pictograms which can
communicate a process.\\\hline 
PictoCreator  	   	& Allows the user to manually create pictograms which can be
saved on the database.\\\hline
PictoReader	   		& A tool which can read the text of an associated pictrogram
aloud.\\\hline
LifeStories	   		& A tool which allows a citizen to describe their day using
pictograms.\\\hline 
Timer     	   		& Allows guardians to create create a timer which limits how
long a citizen can use an application.\\\hline 
Weekplanner 		& Allows for the creation of schedules for citizens
using pictograms. \\\hline 
Category Tool		& A tool which allows pictograms to be grouped together as a
specific category. \\\hline 
Category Game   	& A game which teaches citizens to associate different object
by a common feature. \\\hline 
Voice Game  		& A game which allows citizens to control an object using their
voice volume. \\\hline
\end{tabular}
\label{GApps} 
\caption{The applications available to GIRAF}
\end{table}

The previous semester ended with the Voice Game application working as a
standalone in an acceptable state. The other applications are in working state,
but have several issues, such as bugs and missing features, which prohibit their
use by the customer.\nl

Based on the experiences passed down from the previous semester's students, we
have chosen to make use of an agile developement process, where each group is organized
through the use of Scrum. In other words, this semester we have organized the
multi-project as a scrum of scrums. One group serves as the scrum master while
the remaining 6 groups each send 1 member. These 10 people meet once every week
to discuss the multi-project and after each sprint decide which tasks from the
product backlog are suitable for the sprint backlog. They then further divide
the sprint backlog among the groups such that each group have a suitable number
of tasks for each sprint.\nl

Based on this development framework, this report will be used to document and
reason about the different needed improvements, which have been assigned to our
group, SW609.
  
\section{Initial Problem}
During the initial phases of the project we had a meeting with representatives
from one of the institutions which use GIRAF on a daily basis. Based on their
feedback on the curret state of the system, we have made the following list of
improvements, which are considered essential for the success of this years
developement of the GIRAF project.

\begin{enumerate}
  \item We need to get the weekplanner into a acceptable state, where it can be
  used reliably by the citizens with no unexpected errors occuring. It also
  needs to have the necessary functionality to satisfy the customer.
  \item We need the server to be reliable and store the data safely, this is
  considered necessary since it would otherwise be to use GIRAF in any sizable
  institution.
\end{enumerate}

These requirements form a framework for developing what we consider to be a
``minimum viable product''. In order to further elaborate upon the requirements
and to better be able to divide the project into areas of responsibility, we
made the following list:

\begin{itemize}
  \item Implement an acceptable version of the app ``Weekplanner''
  	\begin{enumerate}
  		\item Fix possible crashes
  		\item Identify problems in Weekplanners dependencies
  		\item Fix bugs in the launcher App
	\end{enumerate}
  \item Simplify the database communication system
   	\begin{enumerate}
  		\item Allow for syncronization of data
  		\item Increase safety of stored data
  		\item Create a useful base for future student to improve
	\end{enumerate}
\end{itemize}

% \section{Development Method}
% This semester the multi-project is a collaboration between 7
% different groups. Through a meeting with one of the customers it is
% decided that the goal of the project is to make a minimal viable product. The
% focus this semester is two part: 
% \begin{enumerate}
%   \item We need to get the weekplanner into a acceptable state, where it can be
%   used reliably by the citizens with no unexpected errors occuring. It also
%   needs to have the necessary functionality to satisfy the customer.
%   \item We need the server to be reliable and store the data safely, this is
%   considered necessary since it would otherwise be to use GIRAF in any sizable
%   institution.
% \end{enumerate}

The groups are divided among the goals according to the desires of each group.
This is meant to increase the quality of the work since each group is able to
specialize on a specific part. It also allows the groups to work easier together
since most of them share some common feature. These two goals lead to the
following distribution of labour:

\begin{table}[H]
\centering
\begin{tabular}{|p{2cm}|p{3cm}|p{8cm}|}
\hline
Group & Focus & Description \\ \hline
SW609 & Weekplanner depedencies & Works on the providing stability to
weekplanner and its dependencies.\\\hline 
SW610 & Weekplanner & Works on getting weekplanner into a working
state.\\
\hline SW611 & Scrum masters & Organizes the scrum meetings. \\\hline 
SW612 & Product owners & Creates and describes tasks, also acts as contact to
customers. \\\hline 
SW613 & REST client & \\ \hline

SW614 & Infrastructure & \\ \hline

SW615 & REST server & \\ \hline

\end{tabular}
\caption{The focus of each of the groups}
\label{GroupDivision}
\end{table}

%Mere specifict om vores gruppes identitet dette semester
% Our focus this semester is as seen above in \autoref{GroupDivision} on
% providing stability to the weekplanner app as well as its dependencies\ldots


As can be seen in \autoref{GroupDivision}, in this project, our group will focus
on improving the stability of the GIRAF project, through the fixing of bugs and
refactoring of code written by the previous bachelor students. As the project is
divided into a number of sprints, \autoref{} is used to document our tasks in
the initial sprint of the project. Furthermore, as this semester focuses on
teamwork and organizing groups of developers, we will touch upon how the
different groups will work together and which tools are used to achieve this
unified development process.

%---------------------------------------------------------------------------
% \section{GIRAF}
% This chapter is used to explain what GIRAF is, what the goal of this semester is
% and how the whole project is organized. the initial phase of the project and what the
% different group will have as their primary focus. Furthermore, we will touch
% upon how the different groups will work together and which tools are used.
% 
% 
% % this section/chapter should be used to describe the project in a multi-project
% % setting
% %This includes an analysis of organizational context
% \section{What is GIRAF}
% \fix{}{Verify application names}
% GIRAF is tablet environment for android. It is aimed at providing citizens and
% their guardians with an easy way to communicate, by providing daily schedules,
% games and education. It is a project which has been worked on over multiple
% years as part the 6'th semesters bachelor project for Software. At the end of
% the semester, the project is left for next batch of students to continue working
% on. GIRAF consists of many different applications, as can be seen in
% \autoref{GApps}.
% 
% \begin{table}[H]
% \centering
% \begin{tabular}{|p{3cm}|p{9cm}|}
% \hline
% Application			& Description \\\hline
% Launcher  			& The main application of GIRAF, controls access to other
% GIRAF applications. \\\hline 
% Sequence	       	& A tool to create a sequence of pictograms which can
% communicate a process.\\\hline 
% PictoCreator  	   	& Allows the user to manually create pictograms which can be
% saved on the database.\\\hline
% PictoReader	   		& A tool which can read the text of an associated pictrogram
% aloud.\\\hline
% LifeStories	   		& A tool which allows a citizen to describe their day using
% pictograms.\\\hline 
% Timer     	   		& Allows guardians to create create a timer which limits how
% long a citizen can use an application.\\\hline 
% Weekplanner 		& Allows for the creation of schedules for citizens
% using pictograms. \\\hline 
% Category Tool		& A tool which allows pictograms to be grouped together as a
% specific category. \\\hline 
% Category Game   	& A game which teaches citizens to associate different object
% by a common feature. \\\hline 
% Voice Game  		& A game which allows citizens to control an object using their
% voice volume. \\\hline
% \end{tabular}
% \label{GApps} 
% \caption{The applications available to GIRAF}
% \end{table}
% 
% 
% 
% The previous semester ended with the Voice Game application working as a
% standalone in an acceptable state. The other applications are in working state,
% but have several issues which prohibit their use by the customer.








\subsection{Organizational Method}

%scrum section
The groups are organized by scrum, one group serves as the scrum masters while
the remaining 6 groups each send 1 member. These 10 people meet once every week
to discuss status of multi-project and how each of the groups are progressing.


%sprint section
The multi-project is divided into 4 different sprints,
They also decide which tasks should be added to each of the groups backlog at
the start of each sprint.


First sprint 20/2 - 15/3 	(3 uger 2 dage)
Second sprint 15/3 - 7/4 	(3 uger 2 dage)
Third sprint 7/4 - 1/5		(3 uger 2 dage)
Fourth sprint 1/5 - 22/5 	(3 uger)
Delivery 29/5


the
multi-project and after each sprint decide which tasks from the product backlog are suitable
for the sprint backlog. They then further divide the sprint backlog among the
groups such that each group have a suitable number of tasks for each sprint.\nl


\section{Tools}

Phabricator

Git

GIRAF website

Discord

Android studio?

Code review?
